Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-02 GWLDCII.tex
started on intro revisions

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper was to enumerate the positroid cells that could be associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.

In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}. This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}. Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$. This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}. Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron, \hlfix{which is useful for ...}{we need a vague one-line description here}. Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.

>>>>

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate (without identifying) the positroid cells that associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.

In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}. This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}. Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$. This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}. Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron. This both gives a novel and elegant interpretation of scattering Amplitudes for this theory, as well as a means of simplifying the calculations greatly from traditional Feynman diagram approaches. Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
